Data Management for LSST Special Programs

### 2023-10-18 sec_proc.tex
minor updates

\item \textbf{{\tt DiaObject} histories may become too large for the sizing model.}
Alert packets contain the full records of all associated 
{\tt DiaSources} from the past 12 months, but the alert
stream bandwidth is sized for the expected histories for
WFD program fields. 
The Prompt pipeline resources are also sized for the
WFD program, and it might not be possible to load up
thousands of epochs at a time.
The Data Management team will have to test the realized
capabilities of Prompt processing and alert distribtuion,
and potentially impose a mitigation strategy such as
limiting histories to the last $N$ observations instead
of the last 12 months in heavily-observed regions.

\item \textbf{The association of {\it new} {\tt DiaSources} into {\tt DiaObjects} 
may be compromised.}
For consecutive images, processing for the second image begins when the processing for the 
first image is only halfway done.
At this point, the {\tt DiaObject} catalog has 
not yet been updated with the new {\tt DiaSources} detected in the first image.
Thus, the {\tt DiaSource}s from images one and two for a new transient 
would not be associated with a single {\tt DiaObject}, but instead would 
each instantiate a new {\tt DiaObject}.

@@

\item \textbf{Possible and necessary:}
in order to detect high-redshift (faint) galaxies in the DDFs,
Rubin Data Management uses the LSST Science Pipelines to deeply
coadd images for each field, and store the results of source
detection and characterization in unique and separate tables that
are included in the annual data release (Section~\ref{ssec:proc_rdm_ddf}).

\item \textbf{Possible but not necessary:}
a time-domain mini-survey that uses standard visits \emph{could}
have separate difference-image analysis object and source catalogs
generated, but this is not necessary as the science goals for the
mini-survey can be met by processing its data with regular Prompt
Processing (Section~\ref{ssec:sci_pproc}), and ensuring the
data is properly labeled (Section~\ref{ssec:sci_labels}).

@@

\item \textbf{Necessary but not possible:}
in order to find the most distant, faint Kuiper Belt Objects in the DDF,
a specialized, computationally intensive form of ``shift-and-stack" processing
is required for detection, but such algorithms are not used by the 
LSST Science Pipelines and so User-Generated Processing will be needed (Section~\ref{ssec:SPCS_TNO}).
A second example here is a twilight survey that uses non-standard visits 
which are outside the boundaries of what the LSST
Science Pipelines can process (Section~\ref{ssec:proc_bounds}).

@@

Further examples of Special Processing are provided below.

\subsubsection{Deep Drilling Fields (DDFs)}

@@

Further examples of User-Generated Processing are provided below.

>>>>

\item \textbf{DIA Object histories may become too large for the sizing model.}
Alert packets contain the full records of all associated 
{\tt DiaSources} from the past 12 months, but the alert
stream bandwidth is sized for the expected histories for
WFD program fields. 
The Prompt pipeline resources are also sized for the
WFD program, and it might not be possible to load up
thousands of epochs at a time.
The Data Management team will have to test the realized
capabilities of Prompt processing and alert distribtuion,
and potentially impose a mitigation strategy such as
limiting histories to the last $N$ observations instead
of the last 12 months in heavily-observed regions.

\item \textbf{The association of new DIA Sources into DIA Objects may be compromised.}
For consecutive images, processing for the second image begins when the processing for the 
first image is only halfway done.
At this point, the {\tt DiaObject} catalog has 
not yet been updated with the new {\tt DiaSources} detected in the first image.
Thus, the {\tt DiaSource}s from images one and two for a new transient 
would not be associated with a single {\tt DiaObject}, but instead would 
each instantiate a new {\tt DiaObject}.

@@

\item \textbf{Possible and necessary:}
in order to detect high-redshift (faint) galaxies in the DDFs,
Rubin Data Management uses the LSST Science Pipelines to deeply
coadd images for each field, and store the results of source
detection and characterization in unique and separate tables that
are included in the annual data release.

\item \textbf{Possible but not necessary:}
a time-domain mini-survey that uses standard visits \emph{could}
have separate difference-image analysis object and source catalogs
generated, but this is not necessary as the science goals for the
mini-survey can be met by processing its data with regular Prompt
Processing, and ensuring the data is properly labeled.

@@

\item \textbf{Necessary but not possible:}
in order to find the most distant, faint Kuiper Belt Objects in the DDF,
a specialized, computationally intensive form of ``shift-and-stack" processing
is required for detection, but such algorithms are not used by the 
LSST Science Pipelines and so User-Generated Processing will be needed.
A second example is a twilight survey that uses non-standard visits 
which are outside the boundaries of what the LSST Science Pipelines can process.

@@

Further examples of potential Special Processing for anticipated Special Programs are provided below.

\subsubsection{Deep Drilling Fields (DDFs)}\label{sssec:proc_special_ddf}

@@

Further examples of potential User-Generated Processing for anticipated Special Programs are provided below.
